Homicide Increases in the COVID-19 Era

### 2025-02-20 Draft1.qmd
Fixed destination

```{r}
library(sf)
library(tidygeocoder)
zcta <- read_sf(dsn = "cb_2020_us_zcta520_500k", layer = "cb_2020_us_zcta520_500k")
LA_zctas <- read.csv("Raw_Data/zctas.csv") #obtained using zipcodeR::search_city("Los Angeles", "CA") and then checking which zip codes are also ZCTAs

>>>>

```{r}
library(sf)
library(tidygeocoder)
zcta <- read_sf(dsn = "Raw_Data/cb_2020_us_zcta520_500k", layer = "cb_2020_us_zcta520_500k")
LA_zctas <- read.csv("Raw_Data/zctas.csv") #obtained using zipcodeR::search_city("Los Angeles", "CA") and then checking which zip codes are also ZCTAs
